Extreme Digitisation For Ground-Based Cosmic Microwave Background Experiments

### 2018-09-23 digitisation.tex
Editing and put in preliminary plots

Observations of the cosmic microwave background (CMB) have played a key role in cosmology \citep{penzias1965, smoot1992, bennett2013, sptpol2013, planck2018}. They can measure the relativistic number of species and the neutrino mass sum. Current CMB Experiments target science goals such as the discovery of inflationary gravitational waves, measuring the relativistic number of species and the neutrino mass sum, and mapping the large-scale distribution of matter through gravitational lensing and the Sunyaev-Zeldovich (SZ) effects. Through lensing and the SZ effects the CMB probes structure formation, reionisation, and is a powerful test for dark matter and dark energy models \citep{s4sciencebook, core2011, litebird2016, pixie2011}.

@@

We find the appropriate normalisation constants for power spectra of few bit TOD as described in the appendix. As seen in Figure \ref{fig:psrecover} all spectra of extremely digitised data recover the input to a satisfying degree. Differences between few bit and the input power spectra are due to observing a single CMB realisation and residual boundary effects.

@@

\begin{figure}[htb]\centering
\includegraphics[width=0.5\textwidth,clip]{Plots/psrecovery.pdf}
  \caption[Current ]{
  Input power spectra used to generate the CMB template maps plus detector noise level (black) and power spectra using 3 bit TOD (violet). A simulations with $1,024,000$ hits per map pixel is shown in this plot. No qualitative differences are visible for other depths of observation.
\label{fig:psrecover}
}
\end{figure}

@@

\begin{figure}[htb]\centering
\includegraphics[width=0.5\textwidth,clip]{Plots/diffwn.pdf}
  \caption[Current ]{
  Power spectra of reconstructed minus input maps for one-bit (green), two-bit (orange), three-bit (violet) and the control case (black) rebined to $\Delta \ell = 100$. No angular scale dependence is observed for all depths of observation. A simulation with $1,024,000$ hits per map pixel is shown.
\label{fig:diffpswn}
}
\end{figure}

@@

>>>>

Observations of the cosmic microwave background (CMB) have played a key role in cosmology \citep{penzias1965, smoot1992, bennett2013, sptpol2013, planck2018}. Current CMB Experiments target science goals such as the discovery of inflationary gravitational waves, measuring the relativistic number of species and the neutrino mass sum, and mapping the large-scale distribution of matter through gravitational lensing and the Sunyaev-Zeldovich (SZ) effects. Through lensing and the SZ effects the CMB probes structure formation, reionisation, and is a powerful test for dark matter and dark energy models \citep{s4sciencebook, core2011, litebird2016, pixie2011}.

@@

We find the appropriate normalisation constants for power spectra of few bit TOD as described in the appendix. As seen in Figure \ref{fig:psrecover} (appendix) all spectra of extremely digitised data recover the input to a satisfying degree. Differences between few bit and the input power spectra are due to observing a single CMB realisation and residual boundary effects.

@@

@@

\begin{figure}[htb]\centering
\includegraphics[width=0.5\textwidth,clip]{Plots/diffwn.pdf}
  \caption[Current ]{
  Power spectra of reconstructed minus input maps for one-bit (green), two-bit (orange), three-bit (violet) and the control case (black) rebined to $\Delta \ell = 400$. No angular scale dependence is observed for all depths of observation. A simulation with $1,024,000$ hits per map pixel is shown.
\label{fig:diffpswn}
}
\end{figure}

@@

\begin{figure*}[h!t]\centering
\vspace{-1cm}
\includegraphics[width=0.8\textwidth,clip]{Plots/psrecovery.pdf}
  \caption[Current ]{
  Input power spectra used to generate the CMB template maps plus detector noise level (black) and digitisation noise (gray) and power spectra using three (violet), two (orange), and one (green) bit TOD. Spectra are rebined to $\Delta \ell = 100$. Main panels are the calculated power spectra binned to $\Delta \ell = 100$, accompanying panels show the difference between the corresponding input plus noise curves and the $C_\ell$ of digitised TOD. Variations occur because only observe a single CMB realisation. A simulations with $1,024,000$ hits per map pixel is shown in this plot. No qualitative differences are visible for other depths of observation.
\label{fig:psrecover}
}
\end{figure*}
